### 2023-04-22 chapters/01-introduction.tex
Put literature citation to appropriate sections

\chapter{Introduction}
\textbf{Following is very coarse draft!}
Manufacturing is experiencing a shift in the traditional asset operational status evaluation and utilization. The goal is to promote safety and production efficiency when the useful life of machine moving parts is extended. In the factories and logistics where this sort of equipment is vital, there is a trend to be able to monitor the health of the machinery parts and above that to diagnose the fault in time to repair it without additional costs. Vibrations are the most nonintrusive way where such faults can be sensed and appear distinctly for an analyst to identify the root cause of the malfunction.

In critical circumstances, such measurements are already in place in some form, but in order to reach wider acceptance, and not remain just a quirk/trend system has to be sufficiently independent, reliable, and as self-sufficient as the model design allows it to be.

The thesis is structured in a following manner. In Chapter 1 we explore the theoretical (analytical) model view, mechanical maintenance approaches, and industry standards where common fault identification is described. Chapter 2 is all about taking vibration measurements (procuring) and transforming them into features meaningful in automatic fault pattern recognition. The methods for ranking are reviewed to obtain the most important and correlated features with machine health status. We delve into modes of diagnosis based on reduced relevant indicators in chapter 3. Chapter 4 takes a look into IoT communication infrastructure limiting the data throughput and devices that can be deployed (accommodate) in the factory environment. Chapter 5 defines measurement vectors and proposes processing steps to diagnose the reoccurring failure, RUL (remaining useful life), and fault types. The approach taken is evaluated and deployed in Chapter 6.

>>>>

\chapter{Introduction}
Manufacturing is experiencing a shift in the traditional practices of asset operational status evaluation and utilization. The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources. The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipment wear and tear. The corrective action be it repair or replacement should be taken on time in response to the key indicators.

The goal is to preserve required safety and production efficiency when extending the useful life of machine moving parts. In the factories and logistics where this sort of equipment is vital, there is a rising interest in the ability to monitor in real-time the health of the machines and to proactively diagnose the fault to repair it without adding unnecessary costs.

Vibrations are the most nonintrusive way with which such faults can be sensed. The experts use it to distinguish faulty states and to identify the malfunction's root cause. In critical circumstances such as in the case of the large turbines in the power plants, the precautions leading to regular machinery check-ups are already in place. To reach wider acceptance and spread, the monitoring solution has to be sufficiently independent, reliable, and as self-sufficient as the model design allows it to be.

The main issue to consider in large-scale machinery monitoring using vibrations are lots of uninformative streams of samples not directly useful for the production line operator. The dashboard must aggregate these flows into trend variables with severity levels categorized based on industrial standards. The majority of signals are viewed once at the maximum therefore to store or even transmit them from the edge device in its entirety would be wasteful. The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan on battery power and preferably remain physically small to reduce the additional clutter.

Attempted machine and deep learning approaches have the crucial impediment that the construction of every single machine is unique to some extent because of tolerances and variable load. The model must be trained specifically for the target environment to achieve the ideal performance. In addition, the failures are relatively rare events occurring usually in the span of multiple months. In these circumstances, it is hard to obtain a large enough sample of fault events quickly. Novelty detection is a technique that can be applied in this case.

The thesis is organized in the following manner. In the first chapter of analysis in section 1 we explore the mechanical maintenance approaches and industry standards on common fault identification. Then section 2 is all about measuring vibrations and transforming them into features meaningful in automatic fault pattern recognition. In section 3 we delve into modes of diagnosis based on reduced relevant indicators. Section 4 deals with evaluation datasets used to determine computational requirements
on IIoT infrastructure. Chapter 2 defines data format and proposes processing steps to diagnose the imminent failure and different fault types. The approach taken is evaluated and validated in Chapter 6.

### 2023-04-22 chapters/analysis/A-CdM.tex
Put literature citation to appropriate sections

\chapter{Problem analysis}

@@

@@

\subsection{Technical standards}
\paragraph{ISO 20816}
Part 1
\begin{itemize}
\item Measurement units - displacement, velocity, acceleration
\item RMS, and max. amplitude = severity
\item Measurement points for sensors (axial, radial) - image, and 45 degrees
\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model
\item Opeartional limits - Alarm, Trips
\end{itemize}

\paragraph{ISO 13373}
\begin{itemize}
\item Sensor mount type in relation to sensor resonance
\item Data presentation - standard display formats for analysis - trends, watefall plots ...
\item Potencial causes for faults (p. 45) - use in vibration fault types
\end{itemize}

\section{Feature engineering}
Large domain knowledge with compared to other areas of machine learning (mechanics - physics)
\subsection{Preprocessing}
\begin{itemize}
\item Detrending - DC removal filter
\item Time synchronous averaging
\end{itemize}

\subsection{Feature extraction}

\paragraph{Statistical measures}
\begin{itemize}
\item Standard Deviation
\item Max. amplitude
\item RMS amplitude
\item Skewness
\item Kurtosis \\
---
\item Spectral centroid
\item RMS frequency
\item Root variance frequency
\item Spectral kurtosis / Fast kurtogram
\item Harmonics (peaks)
\item Spectral Envelope
\item Harmonic spectral deviation \\
---
\item Energy
\item Spectral negentropy
\item TKEO - Teager-Kaiser energy operator
\end{itemize}

\paragraph{Signal decompositions - sparse approximations}
Matching pursuit algorithm optimalization problem
\begin{itemize}
\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging (cite BP)
\item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform)
\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
\item EWT - Empirical Wavelet Transform - (Meyer wavelet) 
\end{itemize}

\subsection{Feature transformation}
\begin{itemize}
\item Principal Component Analysis (PCA)
\item Log transformation (Box-Cox Transform) to normal distribution
\item Normalization (min-max, standardize) 
\end{itemize}

\subsection{Feature selection}
Filter method - SelectKBest  in evaluation phase
\begin{itemize}
\item Variance Threshold
\item Pearson correlation
\item ANOVA F-value
\item Mutal information
\item Fisher score
\item Spectral feature selection algorithm (SPEC)
\end{itemize}

\section{Diagnostics techniques}
Idenification of faulty states in data streams in semi-supervised learning
\subsection{Novelty detection}
\begin{itemize}
\item Local Outlier Factor, Local Correlation Integral (Anomaly score)
\item DenStream (Density based clustering - DBSCAN)
\item Half-space Trees (Isolation forest)
\end{itemize}

\subsection{Classification}
\begin{itemize}
\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Mahalanobis distance / Cosine similarity /  RBF similarity
\end{itemize}

\section{Evaluation Datasets}
(Pictures of machines)

\paragraph{MAFAULDA}\\
SpectraQuest's Machinery Fault Simulator (MFS) Alignment-Balance-Vibration (ABVT)
50 kHz, 5 sec. recordings, Imbalance, Horizontal/Vertical misalignment, Bearings (Overhang / Underhang) - Inner, Outer, Cage

\paragraph{CWRU}
2 HP (1.492 kW) Reliance Electric motor
Bearings - Inner, Outer
12 kHz, 48 kHz
fan and drive end bearings
Fault diameters of 7 mils, 14 mils, 21 mils, 28 mils, and 40 mils (1 mil=0.001 inches) in diameter were introduced separately at the inner raceway, rolling element (i.e. ball) and outer raceway. 
Faulted bearings were reinstalled into the test motor and vibration data was recorded for motor loads of 0 to 3 horsepower (motor speeds of 1797 to 1720 RPM).

\paragraph{Rotating Shaft}
Shaft -  unbalances of different sizes
4 kHz

\section{Sensor and microcontroller}

>>>>

@@

% Automatic Anomaly Detection in Vibration Analysis Based on Machine Learning Algorithms
\cite{torres_automatic_2022}
% Practical Machinery Vibration Analysis and Predictive Maintenance
\cite{scheffer_practical_2004}
% Machinery Condition Monitoring: Principles and Practices
\cite{mohanty_machinery_2015}
% Techniques for Vibration Monitoring
\cite{davies_techniques_2012}
% Technická diagnostika
\cite{ziaran_technicka_2013}
% The experimental application of popular machine learning algorithms on predictive maintenance and the design of IIoT based condition monitoring system
\cite{cakir_experimental_2021}
% Vibration Guide
\cite{noauthor_vibration_2000}

% Bandsaws
% Vibration of bandsaws
\cite{lengoc_vibration_1990}
% Study on Online Detection and Fault Diagnosis of Band Saw Equipment
\cite{chen_study_2014}

@@

\subsection{Technical standards}
\paragraph{ISO 20816}
% ISO 20816-1:2016 - Mechanical vibration - Measurement and evaluation of machine vibration - Part 1: General guidelines
\cite{noauthor_iso_2016}
Part 1
\begin{itemize}
\item Measurement units - displacement, velocity, acceleration
\item RMS, and max. amplitude = severity
\item Measurement points for sensors (axial, radial) - image, and 45 degrees
\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model
\item Opeartional limits - Alarm, Trips
\end{itemize}

\paragraph{ISO 13373}
% ISO 13373-1:2002 - Condition monitoring and diagnostics of machines - Vibration condition monitoring - Part 1: General procedures
\cite{noauthor_iso_2016}
% ISO 13373-2:2016 - Condition monitoring and diagnostics of machines - Vibration condition monitoring - Part 2: Processing, analysis and presentation of vibration data
\cite{noauthor_iso_2016-1}

\cite{jack_d_frequency_nodate}
\begin{itemize}
\item Sensor mount type in relation to sensor resonance
\item Data presentation - standard display formats for analysis - trends, watefall plots ...
\item Potencial causes for faults (p. 45) - use in vibration fault types
\end{itemize}

### 2023-04-22 chapters/analysis/D-Datasets.tex
Put literature citation to appropriate sections

\chapter{Problem analysis}

\section{Condition monitoring}
Why monitor with vibrations, Wear process curve, Fault - failure, Levels are dependant on load and lifecycle stage

\subsection{Maintenance strategies}
\paragraph{Reactive}
\paragraph{Preventive}
\paragraph{Predictive}
- value for the factory and assess risks asociated with potencial fault to assign them importance

\paragraph{Diagnosis indicators} - what we montitor? - when it fails and early signs of faulty component
- RUL (Remaining useful life) models - disadvantage lot of similiar machines (homogenous) or lots of runns until failure
\begin{itemize}
\item Similarity
\item Degradation - used by standards
\item Survival
\end{itemize}

\subsection{Vibration fault types}
- frequency ranges 1 - 300 Hz (shaft), 300 - 1000 Hz, 1000 - 10000 Hz (early bearings)
- Base analytical models: Jeffcott rotor - rotor dynamics, Bearnings model
- Resonance frequencies of each part - machine must run at speeds not aligned with resonance frequencies - Campbell diagram - task for mechanical engineers
- Faults - reasons and frequency content
\begin{itemize}
\item Synchrounous response - based on RPM
\item Mass unbalance
\item Misalignment
\item Eccentricity
\item Bent or bow shaft
\item Cracked shaft
\item Rotor rubs - friction
\item Looseness
\item Auxiliery mechanical systems: Gearbox, Bearings, Belt 
\end{itemize}

\subsection{Technical standards}
\paragraph{ISO 20816}
Part 1
\begin{itemize}
\item Measurement units - displacement, velocity, acceleration
\item RMS, and max. amplitude = severity
\item Measurement points for sensors (axial, radial) - image, and 45 degrees
\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model
\item Opeartional limits - Alarm, Trips
\end{itemize}

\paragraph{ISO 13373}
\begin{itemize}
\item Sensor mount type in relation to sensor resonance
\item Data presentation - standard display formats for analysis - trends, watefall plots ...
\item Potencial causes for faults (p. 45) - use in vibration fault types
\end{itemize}

\section{Feature engineering}
Large domain knowledge with compared to other areas of machine learning (mechanics - physics)
\subsection{Preprocessing}
\begin{itemize}
\item Detrending - DC removal filter
\item Time synchronous averaging
\end{itemize}

\subsection{Feature extraction}

\paragraph{Statistical measures}
\begin{itemize}
\item Standard Deviation
\item Max. amplitude
\item RMS amplitude
\item Skewness
\item Kurtosis \\
---
\item Spectral centroid
\item RMS frequency
\item Root variance frequency
\item Spectral kurtosis / Fast kurtogram
\item Harmonics (peaks)
\item Spectral Envelope
\item Harmonic spectral deviation \\
---
\item Energy
\item Spectral negentropy
\item TKEO - Teager-Kaiser energy operator
\end{itemize}

\paragraph{Signal decompositions - sparse approximations}
Matching pursuit algorithm optimalization problem
\begin{itemize}
\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging (cite BP)
\item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform)
\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
\item EWT - Empirical Wavelet Transform - (Meyer wavelet) 
\end{itemize}

\subsection{Feature transformation}
\begin{itemize}
\item Principal Component Analysis (PCA)
\item Log transformation (Box-Cox Transform) to normal distribution
\item Normalization (min-max, standardize) 
\end{itemize}

\subsection{Feature selection}
Filter method - SelectKBest  in evaluation phase
\begin{itemize}
\item Variance Threshold
\item Pearson correlation
\item ANOVA F-value
\item Mutal information
\item Fisher score
\item Spectral feature selection algorithm (SPEC)
\end{itemize}

\section{Diagnostics techniques}
Idenification of faulty states in data streams in semi-supervised learning
\subsection{Novelty detection}
\begin{itemize}
\item Local Outlier Factor, Local Correlation Integral (Anomaly score)
\item DenStream (Density based clustering - DBSCAN)
\item Half-space Trees (Isolation forest)
\end{itemize}

\subsection{Classification}
\begin{itemize}
\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Mahalanobis distance / Cosine similarity /  RBF similarity
\end{itemize}

@@

\paragraph{MAFAULDA}\\
SpectraQuest's Machinery Fault Simulator (MFS) Alignment-Balance-Vibration (ABVT)
50 kHz, 5 sec. recordings, Imbalance, Horizontal/Vertical misalignment, Bearings (Overhang / Underhang) - Inner, Outer, Cage

@@

@@

\section{Sensor and microcontroller}

>>>>

@@

\paragraph{MAFAULDA}
SpectraQuest's Machinery Fault Simulator (MFS) Alignment-Balance-Vibration (ABVT)
50 kHz, 5 sec. recordings, Imbalance, Horizontal/Vertical misalignment, Bearings (Overhang / Underhang) - Inner, Outer, Cage

\cite{noauthor_mafaulda_nodate}

@@

% Feature-based performance of SVM and KNN classifiers for diagnosis of rolling element bearing faults
\cite{jamil_feature-based_2021}
% Machine Learning-Based Unbalance Detection of a Rotating Shaft Using Vibration Data
\cite{mey_machine_2020}

@@

\section{Sensor and microcontroller}
% Intelligent Sensor Networks: The Integration of Sensor Networks, Signal Processing and Machine Learning
\cite{hu_intelligent_2012}
